Supplementary Information

### 2020-11-30 doc/manuscript/MEE_manuscript.Rmd
add @camerondow35 as author

[Kristina J. Anderson-Teixeira^1,2^*](0000-0001-8461-9713),
Valentine Herrmann^1^,
Christy Rollinson^3^,
Bianca Gonzalez^1^,
Erika B. Gonzalez-Akre^1^,
Neil Pederson^4^,
Camille Piponiot^1,2^,
Ross Alexander,
Craig D. Allen,
Raquel Alfaro-Sánchez^wl^,
Tala Awada,
Jennifer L. Baltzer^wl^,
Patrick J. Baker,
Sarayudh Bunyavejchewin,
Paolo Cherubini,
Justin Cooper,
Stuart J. Davies^2^,
Ryan Helcoski^1^,
[Jakub Kašpar^cz^](0000-0003-1780-6310),
James Lutz,
Ellis Q. Margolis,
Justin Maxwell^jm^,
Sean McMahon^2^,
Sabrina Russo,
[Pavel Šamonil^cz^](0000-0002-7722-8797),
Anastasia Sniderhan^wl^,
Alan J. Tepley^1,at^,
[Ivana Vašíčková^cz^](0000-0002-6070-5956), 
Mart Vlam,
Peter Zuidema

@@

- at HKK, @nock_longterm_2011 observed decreases in BAI (by standardized size classes) over time
- dramatic growth declines at LT and SC are consistent with increasing tree mortality

@@

- In stands with no known stand-clearing disturbance within or shortly prior to the analysis time frame (ZOF?, NM?, CB, SC), trends would represent more gradual successional trends or responses to global change.
- At NM and SC, rapid declines in growth make sense in light of rapid climate change. They also correspond to observations of high tree mortality rates.
- At ZOF and CB,  trends are more mixed...
~~~~

@@

*(growth rate should respond strongly to a tree's relative DBH within a site, which we don't have going back in time)*

>>>>

[Kristina J. Anderson-Teixeira^1,2^*](0000-0001-8461-9713),
Valentine Herrmann^1^,
Christy Rollinson^3^,
Bianca Gonzalez^1^,
Erika B. Gonzalez-Akre^1^,
Neil Pederson^4^,
Camille Piponiot^1,2^,
Ross Alexander,
Craig D. Allen,
Raquel Alfaro-Sánchez^wl^,
Tala Awada,
Jennifer L. Baltzer^wl^,
Patrick J. Baker,
Sarayudh Bunyavejchewin,
Paolo Cherubini,
Justin Cooper,
Stuart J. Davies^2^,
Cameron Dow^1^,
Ryan Helcoski^1^,
[Jakub Kašpar^cz^](0000-0003-1780-6310),
James Lutz,
Ellis Q. Margolis,
Justin Maxwell^jm^,
Sean McMahon^2^,
Sabrina Russo,
[Pavel Šamonil^cz^](0000-0002-7722-8797),
Anastasia Sniderhan^wl^,
Alan J. Tepley^1,at^,
[Ivana Vašíčková^cz^](0000-0002-6070-5956), 
Mart Vlam,
Peter Zuidema

@@

- at HKK, @nock_longterm_2011 observed decreases in BAI (by standardized size classes) over time

@@

- In stands with no known stand-clearing disturbance within or shortly prior to the analysis time frame (ZOF?, NM?, CB, SC), trends would represent more gradual successional trends or responses to global change.
- At NM and SC, rapid declines in growth make sense in light of rapid climate change. They also correspond to observations of high tree mortality rates.
- At ZOF and CB,  trends are more mixed...

~~~~

@@

*(growth rate should respond strongly to a tree's relative DBH within a site, which we don't have going back in time/ disentangling DBH and year is tough)*
